\documentclass{article}[12pt]
\usepackage{graphicx}
\usepackage{geometry}[margin=2cm]
\title{Journal 9}
\author{Raja Kantheti}
\begin{document}
\maketitle
\section*{Chages based on reviews: }
I intend to the following changes in each of the mentioned aspects of the paper.
\begin{itemize}
    \item Clarity of Purpose:
    \begin{enumerate}
        \item Adding a cleat statement to reflect the story line I chose.
        \item Be more specific about scope of the paper being a survey followed by novel evaluations for comparisions. 
    \end{enumerate}
    \item Introduction:
    \begin{enumerate}
        \item I will make changes to introduction to be more precise and to the point.
        \item I will add a brief paragraph about what the paper found after my experiments. 
    \end{enumerate}
    \item Audience and Background:
    \begin{enumerate}
        \item I can add more terms I used in the paper to make the reader more familiar about the paper. 
        \item I am not sure if I need to add more background information as the paper is a survey and not a research paper.
        \item I can add a brief paragraph about the audience of the paper.
    \end{enumerate}
    \item Classification and Related Research:
    \begin{enumerate}
        \item I will take the feedback about distinguishing between survey papers and research papers.
        \item I would like to add a brief paragraph about the classification of the papers I surveyed and talk more about the research papers that has information about more advanced mmethods of Branch Prediction.
    \end{enumerate}
    \item Content Analysis and Citations:
    \begin{enumerate}
        \item As I as in the flow of writing I couldn't add more citations, I will add more citations to the paper now in the second draft.
        \item I will add more content on overall comparative analysis of the papers, stating overall trends, improvements or similarities in performmance across differenct approaches. 
    \end{enumerate}
    \item Experimental Setup (Section 5):
    \begin{enumerate}
        \item I will clarify and add more details about the experimental setup and about the rationale behind the experiment, as I am conducting my own.
    \end{enumerate}
    \item Overall Structure:
    \begin{enumerate}
        \item I will revise the paper more for consistency over logical flow from introduction to conclusion. 
        \item I will modify the paper Structure to have more depth and corrected references. 
    \end{enumerate}
    \item Expansion and Detail:
    \begin{enumerate}
        \item I will add more in depth detail in explanation of various techniques. 
        \item I will add references and draw my own conclusions by comparing and contrasting the knowledge from the papers I surveyed.
    \end{enumerate}
\end{itemize}
\end{document}